\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-21 jss/article.tex
correction on 20 Aug

\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\label{fig:pseudo}
\end{center}
\end{figure}

@@

\subsubsection{Simple Unbiased Estimates of Coverage Probabilities}
Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise. Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$. This provides a simple unbiased estimate of the $k$ coverage probabilities. For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased estimate of coverage probability for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$. As the number of pseudo-datasets increases, this simple estimate converges to the true coverage probability of the first group given $A$ and $\beta$.

\subsubsection{Rao-Blackwellized Unbiased Estimates of Coverage Probabilities}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic. Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset. This expectation is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset. We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \beta$) in (\ref{normalpost}). Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\mathbf{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\beta$ are known. Then, we estimate the first group's coverage probability by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.

@@

The output contains information about observed death ratios ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds of interval estimates ($\hat{\lambda}_{j, low}$), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds of interval estimates ($\hat{\lambda}_{j, upp}$), and standard deviations of posterior distribution3 ($sd(\lambda_{j}\vert \textbf{y})$).

As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.02$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight. This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively. If the second level has more information than the first level, \emph{i.e.} ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%. This is clear because, as caseload increases, shrinkage decreases, depending less on the second-level information.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plot(p)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 3in]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
\label{fig:hospshr}
\end{center}
\end{figure}

@@

Intuitively, switching ranks for these two hospitals makes sense. To be specific, their observed death ratios ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602 each. Considering solely the observed death ratios may lead to an unfair comparison because the latter hospital handled twice the caseload. \pkg{Rgbp} accounts for this caseload difference, making the true death rate estimate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.030) much harder than that for the latter hospital. This is what happened to the two left-most hospitals in the first plot.

But the point estimates are not enough to evaluate hospital reliabilities because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other. In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed on the right-hand side. We see that each posterior mean (red dot) is between the sample mean (empty dot) and the second-level mean (a blue horizontal line). For reference, we could plot this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{hospital2.png}
\caption{Coverage plot via frequency method checking for 31 hospitals}
\label{fig:hospitalcoverage}
\end{center}
\end{figure}

In Figure \ref{fig:hospitalcoverage} we see three lines; one is a red line connecting Rao-Blackwellized unbiased estimates for 31 hospitals; another is a dashed blue line connecting simple unbiased estimates for those hospitals; the other is a black horizontal line indicating the confidence level, 0.95.

The estimated overall average coverage rate across all the hospitals is 0.955 from both Rao-Blackwellized. This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling. Note that these estimates depend on the given true value of $r$, the known prior mean, and the assumption that the model is true.

If we want to check average Rao-Blackwellized unbiased estimates for each hospital, the following code gives us such estimates.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.956 0.957 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.955 
[13] 0.955 0.956 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.955 0.955 
[25] 0.955 0.954 0.954 0.954 0.954 0.953 0.953
\end{CodeOutput}
\end{CodeChunk}

As for average simple unbiased estimates for each hospital, we can type the code below.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.955 0.959 0.955 0.949 0.944 0.955 0.960 0.947 0.948 0.962 0.967 0.962 
[13] 0.957 0.959 0.961 0.958 0.957 0.948 0.963 0.963 0.967 0.955 0.968 0.948 
[25] 0.965 0.947 0.955 0.946 0.957 0.948 0.948
\end{CodeOutput}
\end{CodeChunk}

One more thing to mention is the accuracy of Rao-Blackwellized unbiased estimates compared to that of simple ones. Taking the first hospital as an example, we can calculate the sample variance of 1,000 Rao-Blackwellized unbiased estimates for the first hospital and that of 1,000 simple ones by typing following code. For reference, \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual simulation results.
\begin{CodeChunk}
\begin{CodeInput}
R> var(pcv$raw.resultRB[1, ]) / 1000
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.00000245
\end{CodeOutput}
\begin{CodeInput}
R> var(pcv$raw.resultS[1, ]) / 1000
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.00004302
\end{CodeOutput}
\end{CodeChunk}

It shows that Rao-Blackwellized unbiased estimate is about 18 times more accurate than simple one. Also, as the number of simulation increases, the zig-zagging blue line is expected to converge to the red line by the law of large numbers.
% For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.

@@

It is noted that \cite{1995} also investigated a similar ranking problem in hierarchical modeling, taking shrinkage into account.

@@

Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated. It is assumed that the mean for each score is drawn from a common normal distribution and hence, we can use \code{gbp} to fit this Normal-Normal hierarchical model.

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
The output from \code{gbp} provides an easy to read summary of the results of the estimation. In the Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_i = V_i/(V_i + A)$ and as such those schools whose variation within the school is less than between the variation schools will shrink greater than $50\%$. The results provide by \code{gpb} suggests that there is little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0. \pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.

@@

\begin{figure}[h] 
\begin{center}
\includegraphics[width = 3in]{school1.png}
\caption{Shrinkage plot and 95\% interval plot for 8 schools}
\label{fig:8schoolsplot}
\end{center}
\end{figure}

Plotting the results provides a visual aid to understanding but is only largely beneficial when the number of groups $(k)$ is small. In the case where the number of groups is large \pkg{Rgbp} provides a summary feature:

@@

An integral part of fitting any model is to check the method of estimation. Namely we can generate new pseudo-data from our assumed model by fixing the hyper-parameter values ($A$ and $\mu_0$ in this example) at their estimates. It is then possible to simulate ``true'' $\theta_i$ for each group $i$ and re-fit the model numerous times to estimate the coverage probabilities of our procedure.

\begin{CodeChunk}
\begin{CodeInput}
R> gcv <- coverage(g, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{school2.png}
\caption{Coverage plot via frequency method checking for 8 schools}
\label{fig:schoolcoverage}
\end{center}
\end{figure}

As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (black horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example. Note that all the coverage estimates depend on the given true values of $A$ and $\beta_{0}$, and the assumption that the model is true.

In addition, average Rao-Blackwellized unbiased estimates for each school can be seen as below.
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.966 0.957 0.966 0.962 0.960 0.961 0.960 0.969
\end{CodeOutput}
\end{CodeChunk}

@@

All the individual simulation results are saved in \code{gcv$raw.resultRB} and \code{gcv$raw.resultS}, in which each row is about each school.

@@

We see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038). Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all the outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plot(b)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 3in]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
\label{fig:baseball}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bcv <- coverage(b, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball2.png}
\caption{Coverage plot via frequency method checking for 18 players}
\label{fig:baseball2}
\end{center}
\end{figure}

Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.972 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval. Note that each coverage estimate depends on given true values of $r$ and $\beta_{(2\times1)}$, and the assumption that the model is true.

The average Rao-Blackwellized unbiased estimates for each player follows.
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.972 0.972 0.973 0.972 0.972 0.970 0.974 0.972 0.973 0.973 0.973 0.970 
[13] 0.972 0.972 0.973 0.972 0.973 0.972
\end{CodeOutput}
\end{CodeChunk}

And average simple unbiased estimates for each player are
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.969 0.967 0.973 0.980 0.970 0.974 0.965 0.976 0.969 0.972 0.980 0.972 
[13] 0.957 0.969 0.972 0.982 0.978 0.984
\end{CodeOutput}
\end{CodeChunk}

All the individual simulation results are saved in \code{bcv$raw.resultRB} and \code{bcv$raw.resultS}, in which each row is about each player.

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[width=6cm]{process.png}
\caption{Pseudo-data generating process}
\label{fig:pseudo}
\end{center}
\end{figure}

@@

\subsubsection{Simple Unbiased Coverage Estimates}
Let's define an indicator variable, $I^{(i)}_{j}$, which is 1 if the $j$-th group's interval estimate from the $i$-th pseudo-dataset includes $\mu^{(i)}_{j}$ and 0 otherwise. Then \code{coverage} estimates the coverage probability via the sample mean of these indicator variables for each group $j$, averaging over all the possible $\mu^{(i)}_{j}$ and $y^{(i)}_{j}$ for given $A$ and $\beta$. This provides $k$ simple unbiased coverage estimates. For example, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$ is the simple unbiased coverage estimate for the first group ($j=1$), accounting for possible randomness in $\mu^{(i)}_{1}$ and $y^{(i)}_{1}$, $i=1, \ldots, 500,$ given a specific $(A, \beta)$. As the number of pseudo-datasets increases, this simple unbiased coverage estimate converges to the true coverage probability of the first group given $A$ and $\beta$.

\subsubsection{Rao-Blackwellized Unbiased Coverage Estimates}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking a conditional expectation given a sufficient statistic. Based on this idea, we use $E(I^{(i)}_{j}\vert y^{(i)}_{j}, A, \beta$), where $A$ and $\beta$ are given and $y^{(i)}_{j}$ is the sufficient statistic for the $j$-th group in the $i$-th pseudo-dataset. This expectation is the same as Pr$(\hat{\mu}^{(i)}_{j, low}\le \mu^{(i)}_{j} \le\hat{\mu}^{(i)}_{j, upp}\vert y^{(i)}_{j}, A, \beta)$, where ($\hat{\mu}^{(i)}_{j, low}$, $\hat{\mu}^{(i)}_{j, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset. We can calculate this probability  because we know the distribution of ($\mu^{(i)}_{j} \vert y^{(i)}_{j}, A, \beta$) in (\ref{normalpost}). Note that conditioning on $y^{(i)}_{j}$ is equivalent to conditioning on $\mathbf{y}^{(i)}_{(k\times1)}$ as long as $A$ and $\beta$ are known. Then, we estimate the first group's coverage probability by $\frac{1}{500}\sum_{i=1}^{500}E(I^{(i)}_{1}\vert y^{(i)}_{1}, A, \beta)$, which is also unbiased but with smaller variance than the previous simple estimator, $\frac{1}{500}\sum_{i=1}^{500}I^{(i)}_{1}$.

@@

The output contains information about observed death ratios ($y_{j}$), caseloads ($n_{j}$), known prior mean ($\lambda_{0}$), shrinkage estimates ($\hat{B}_{j}$), lower bounds (2.5\% percentiles of posterior distributions if 95\% confidence level is given) of interval estimates ($\hat{\lambda}_{j, low}$), posterior means ($\hat{\lambda}_{j}=E(\lambda_{j}\vert \textbf{y})$), upper bounds (97.5\% percentiles of posterior distributions) of interval estimates ($\hat{\lambda}_{j, upp}$), and standard deviations of posterior distributions ($sd(\lambda_{j}\vert \textbf{y})$).

As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.030$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight. This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree (sample sizes) of prior and observed information respectively. If the second level has more information than the first level, \emph{i.e.} ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%. This is clear because, as caseload increases, shrinkage decreases, depending less on the second-level information.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plot(p)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 6in]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot for 31 hospitals}
\label{fig:hospshr}
\end{center}
\end{figure}

@@

Intuitively, switching ranks for these two hospitals makes sense. To be specific, their observed death rates ($y_{j}$, $j=8, 23$) are 0.0136 and 0.0150 and caseloads ($n_{j}$, $j=8, 23$) are 295 and 602 each. Considering solely the observed death rates may lead to an unfair comparison because the latter hospital handled twice the caseload. \pkg{Rgbp} accounts for this caseload difference, making the true death rate estimate for the former hospital shrink toward the state-level mean ($\lambda_{0}$=0.030) much harder than that for the latter hospital. This is what happened to the two left-most hospitals in the first plot.

But the point estimates are not enough to evaluate hospital reliabilities because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other. In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed. We see that each posterior mean (red dot) is between the sample mean (empty dot) and the second-level mean (a blue horizontal line). For reference, we could plot this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 3.5in]{hospital2.png}
\caption{Coverage plot via frequency method checking for 31 hospitals}
\label{fig:hospitalcoverage}
\end{center}
\end{figure}

In Figure \ref{fig:hospitalcoverage}, the black horizontal line at 0.95 represents the nominal confidence level, the smooth red curve connects Rao-Blackwellized (RB) unbiased coverage estimates for 31 hospitals, and the dashed zagged blue curve passes simple unbiased coverage estimates for these hospitals. As the number of simulations increases, the zig-zagging blue curve would be closer to the smooth red curve by the law of large numbers.

The overall RB unbiased coverage estimate across all the hospitals is 0.955. And none of RB unbiased coverage estimates for 31 hospitals are less than 0.95 regardless of their caseloads ($n_{j}$). This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling. Note that these estimates depend on the given true value of $r$, the known prior mean, and the assumption that the model is true.

The following code provides 31 RB unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.956 0.957 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.956 0.955 
[13] 0.955 0.956 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.955 0.955 
[25] 0.955 0.954 0.954 0.954 0.954 0.953 0.953
\end{CodeOutput}
\end{CodeChunk}

And the code below calculates 31 simple unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.955 0.959 0.955 0.949 0.944 0.955 0.960 0.947 0.948 0.962 0.967 0.962 
[13] 0.957 0.959 0.961 0.958 0.957 0.948 0.963 0.963 0.967 0.955 0.968 0.948 
[25] 0.965 0.947 0.955 0.946 0.957 0.948 0.948
\end{CodeOutput}
\end{CodeChunk}

The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined as the square root of $S^{2}_{RB, j}/N_{sim}$, where $S^{2}_{RB, j}$ is the sample variance of 1,000 RB unbiased coverage estimates for the $j$-th hospital. The following code provides 31 standard errors.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0015 0.0015 0.0013 0.0012 0.0012 0.0012 0.0012 0.0012 0.0011 0.0011 0.0011 
[12] 0.0011 0.0010 0.0010 0.0010 0.0010 0.0011 0.0010 0.0010 0.0010 0.0009 0.0010 
[23] 0.0009 0.0009 0.0009 0.0009 0.0008 0.0008 0.0007 0.0006 0.0006
\end{CodeOutput}
\end{CodeChunk}
Similarly, 31 standard errors for each simple unbiased coverage estimate are
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageS
\end{CodeInput}
\begin{CodeOutput}
[1] 0.0063 0.0060 0.0071 0.0063 0.0059 0.0066 0.0063 0.0068 0.0060 0.0076 0.0063 
[12] 0.0059 0.0066 0.0072 0.0070 0.0074 0.0060 0.0062 0.0065 0.0065 0.0075 0.0072 
[23] 0.0061 0.0067 0.0064 0.0065 0.0061 0.0072 0.0067 0.0070 0.0065
\end{CodeOutput}
\end{CodeChunk}

Taking the first hospital as an example, the variance of RB unbiased coverage estimate is about 18 times smaller than that of simple one. It means that 1,000 RB unbiased coverage estimates are as efficient as 18,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.

For reference, \code{raw.resultRB} and \code{raw.resultS}, each row of which is about each hospital, in \code{pcv} contain all the individual simulation results.
% For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.

@@

\cite{1995} also investigated a similar ranking problem in hierarchical modeling, taking shrinkage into account.

@@

Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known. At the second hierarchy, the mean for each school is assumed to be drawn from a common Normal distribution and hence, we can use the Gaussian component of \code{gbp} to fit this Normal-Normal hierarchical model.

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
This output from \code{gbp} summarizes the results. In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_i = V_i/(V_i + A)$. As such schools whose variation within the school ($V_{j}$) is less than the between variation ($A$) schools will shrink greater than $50\%$. The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit because every school's $95\%$ posterior interval contains 0.

@@

\begin{figure}[h] 
\begin{center}
\includegraphics[width = 6in]{school1.png}
\caption{Shrinkage plot and 95\% interval plot for 8 schools}
\label{fig:8schoolsplot}
\end{center}
\end{figure}

\pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}. Plotting the results provides a visual aid to understanding but is only largely beneficial when the number of groups $(k)$ is small. In the case where the number of groups is large \pkg{Rgbp} provides a summary feature:

@@

The method check, assuming the model is correct, generates new pseudo-data from our assumed model. It starts by fixing the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example). We then simulate ``true'' $\theta_j$ for each group $j$ and re-fit the model 1,000 times to estimate the coverage probabilities of our procedure.

\begin{CodeChunk}
\begin{CodeInput}
R> gcv <- coverage(g, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 3.5in]{school2.png}
\caption{Coverage plot via frequency method checking for 8 schools}
\label{fig:schoolcoverage}
\end{center}
\end{figure}

As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (black horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example. Note that all the coverage estimates depend on the chosen true values of $A$ and $\beta_{0}$, and the assumption that the model is valid.

In addition, Rao-Blackwellized (RB) unbiased coverage estimates for each school can be gotten with the command below.
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.966 0.957 0.966 0.962 0.960 0.961 0.960 0.969
\end{CodeOutput}
\end{CodeChunk}

@@

All the simulation results (0-1 coverage and RB coverage estimates) are saved in two $8\times1,000$ matrices, \code{gcv$raw.resultRB} and \code{gcv$raw.resultS}, each row of which is about each school.

@@

We see that the two prior means distinguishing outfielders from other positions are significantly different (p-value = 0.038). Also, the positive sign of $\hat{\beta}_{1}$ indicates that the population mean batting average for all outfielders tends to be higher than that for those in the other positions (estimated odds ratio = exp(0.389)=1.48).

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plot(b)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 6in]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot for 18 baseball players}
\label{fig:baseball}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bcv <- coverage(b, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 3.5in]{baseball2.png}
\caption{Coverage plot via frequency method checking for 18 players}
\label{fig:baseball2}
\end{center}
\end{figure}

Finally, in Figure \ref{fig:baseball2}, we see that the overall Rao-Blackwellized unbiased coverage estimate is 0.972 (across all the players), conservatively satisfying the definition of the 95\% confidence interval. Note that each coverage estimate depends on given true values of $r$ and $\beta_{(2\times1)}$, and the assumption that the model is valid.

The Rao-Blackwellized unbiased coverage estimates and their standard errors for each player follow.
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.972 0.972 0.973 0.972 0.972 0.970 0.974 0.972 0.973 0.973 0.973 0.970 
[13] 0.972 0.972 0.973 0.972 0.973 0.972
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0012 0.0013 0.0012 0.0012 0.0013 0.0011 0.0011 0.0009 0.0012 0.0013 
[11] 0.0010 0.0013 0.0010 0.0012 0.0015 0.0010 0.0010 0.0011
\end{CodeOutput}
\end{CodeChunk}

And simple unbiased coverage estimates and their standard errors for each player are
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.969 0.967 0.973 0.980 0.970 0.974 0.965 0.976 0.969 0.972 0.980 0.972 
[13] 0.957 0.969 0.972 0.982 0.978 0.984
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0045 0.0059 0.0066 0.0049 0.0052 0.0044 0.0042 0.0054 0.0056 0.0053 0.0049 
[11] 0.0056 0.0042 0.0049 0.0056 0.0057 0.0052 0.0052
\end{CodeOutput}
\end{CodeChunk}

All the simulation results are saved in two $18\times1,000$ matrices, \code{bcv$raw.resultRB} and \code{bcv$raw.resultS}, each row of which is about each player.
